Using Semantic Similarity to Assist Assessing MCR Comment Usefulness

### 2014-07-27 sections/introduction.tex
updated more of the introduction...

\dan{Much of the following material should be placed in a separate Motivation section} 
In this paper we present a text mining approach to assisting in classifying the usefulness of comments. The purposed approach is meant to enable classifying the large amounts of MRC comments needed to conduct comment and code quality studies such as those discussed earlier. Manual classification can quickly become an untenable task. Our modest OSS case study has a over 17,000 potentially useful comments. At an optimistic 5 seconds peer comment classification we would expect about 24 person-hours of effort. Furthermore manual classification is subjective and error-prone. By introducing some automation support based on objective empirical criteria, the method we propose here aims to both reduce effort and increase confidence in classification to a degree practical for addressing very large MRC data sets. Because usefulness of a comment is not precisely defined and a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.

We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useful} comment as one that does not. Usefulness is not dichotomous and we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential. In our approach we analyze the similarity between a commit message of the proposed changes and the respective comments that follow. Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar. To do determine these semantic relationships we use the Vector Space Model (VSM) and calculate similarity as the cosine distance between the comment and commit message vectors and the euclidian distance between them to calculate dissimilarity. 
We create our predictive model by estimating pairs of similarity and dissimilarity values that discriminate between useful and useless comments that optimize prediction performance measures such as Precision, Recall and F-measure.

For our case study of the method, we use a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation. For training and validation of our approach, three experts manually classified the usefulness for 320 comments. We also apply our predictive model to the full set of 
17,000 
\dan{what's the actual number?}
comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:

>>>>

\dan{Much of the following material should be placed in a separate Motivation section} 
In this paper we present a text mining approach to assist in classifying the usefulness of comments.
The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.

Our modest OSS case study has a over 17,000 potentially useful comments.
At an optimistic 5 seconds peer comment classification, we would expect about 24 person-hours of effort.
Furthermore, manual classification is subjective and error-prone.

By introducing some automation support based on objective empirical criteria,
the method we propose here aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.

We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless} comment as one that does not.
Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.

In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors. 
We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.

For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
